\documentclass{letter}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
%
\signature{Abel Romer}%
\address{1525 Griffith Park Blvd, Apt. 107 \\ Los Angeles, CA 90026 \\ (707) 913-7014 \\ \texttt{abel.e.romer@gmail.com} \\ \texttt{https://www.abelromer.com}}%
%
\begin{document}%
\normalsize%
\begin{letter}{Hiring Manager \\ Company \\ Street Address \\ City and ZIP}%

Dear Hiring Manager, 
I am a recent (September 2022) graduate with a master’s degree in mathematics, and I am applying for the Senior Full Stack Python Engineer position. My degree required that I produce a novel result in a research topic of my choosing; I examined cellular automata on grids and designed and built a website to test my results, which is live at https://ahblay.pythonanywhere.com.

I bring a varied skill-set and interdisciplinary ability to address and solve problems to your company. My mathematical expertise provides a fluency in analytical and algorithmic thinking, as well as the ability to quickly assess problems from multiple perspectives. I am a quick and passionate learner, and have taught myself full-stack web development and basic electrical engineering and Arduino skills. 

I am experienced in back-end engineering tasks, have contributed to architecture and design decisions, and possess a deep understanding of software development lifecycle processes such as version control, build and configuration management, automated deployments, automated testing, etc. My knowledge includes Python, MySQL, AWS Redshift, Docker, Kubernetes, Argo CD, Design Patterns, RESTful Services, GraphQL, DevOps, and Agile Methodologies.

I am able to quickly learn and apply new technologies to solve difficult problems, think creatively, communicate difficult concepts clearly and concisely, and encourage others to engage deeply with today’s problems. I have the academic curiosity and commitment to comprehensive understanding that you are seeking in this role. 

I am a Green Card Holder or US Citizen, and am physically located in the USA, with the ability to travel to the client office for meetings. 

Thank you for your time and consideration. I am looking forward to hearing from you. 
%
\closing{Sincerely,}%
\encl{Resume}%
\end{letter}%
\end{document}