\documentclass{letter}%
\usepackage[T1]{fontenc}%
\usepackage[utf8]{inputenc}%
\usepackage{lmodern}%
\usepackage{textcomp}%
\usepackage{lastpage}%
\usepackage[left=1.5in,right=1.5in,top=1.25in,bottom=1.25in]{geometry}%
%
\signature{Abel Romer}%
\address{18900 Robinson Rd \\ Sonoma \\ 7078883717 \\ \texttt{abeleromer@gmail.com} \\ \texttt{Website}}%
%
\begin{document}%
\normalsize%
\begin{letter}{Hiring Manager \\ Company \\ Street Address \\ City and ZIP}%
\opening{Dear Hiring Manager:}%
I am a recent graduate with a master’s degree in mathematics and a passion for coding, computer science, and problem-solving. My degree required that I produce a novel result in a research topic of my choosing, for which I utilized cellular automata on grids and built a website to facilitate my research efforts. This website is live at https://ahblay.pythonanywhere.com. 

I bring a varied skill set and an interdisciplinary approach to problem-solving to the role, with my mathematical expertise providing a fluency in analytical and algorithmic thinking, and the ability to quickly assess problems from multiple perspectives. I am a quick and passionate learner with experience in building machine learning (ML) solutions and coding in various languages, such as Python, Scala, Java, and Go. Examples of my self-taught proficiency include creating a neural network from first principles and building an 8-bit computer from resistors and logic gates.

In addition, my technical consulting experience, coupled with my understanding of data warehousing concepts and deep learning frameworks, makes me an ideal candidate for the role. I will bring academic curiosity and a commitment to comprehensive understanding to the position, and I am driven to deeply understand the technologies that we interact with on a daily basis. 

I'm confident I have the skills and abilities to become a trusted technical advisor for customers and solve Machine Learning challenges. I am confident I can create and deliver best practices recommendations, tutorials, blog articles, sample code, and technical presentations to different audiences. I am experienced in working with customers, partners, and Google Product teams to deliver tailored solutions into production, and am happy to mentor customers on the practical challenges in ML systems. I am also willing to travel up to 30% of the time for meetings, technical reviews, and onsite delivery activities.

The listed salary range for this full-time position is well within my expectations, and I am eager to begin this new endeavor. Thank you for your time and consideration.%
\closing{Sincerely,}%
\encl{Resume}%
\end{letter}%
\end{document}